---
title: "Homework 3" 
author: "Noah McIntire"
fontsize: 12pt
geometry: margin=1in
urlcolor: black
output: pdf_document
---

## Problem 1   
### a)
```{r}
mean1<-99.5
std1<-4.8
sig1<-.05
```

### b)
```{r}
zfunc <- function(x){
samp <- rnorm(x, mean=mean1, sd=std1)
smean <- mean(samp)
zTest <- (smean - mean1)/(std1/sqrt(x))
if (abs(zTest)>1.96) {
  return(TRUE)
} else {
  return(FALSE)
}
} 
zfunc(27)
```

### c)
```{r}
repvect <- replicate(10000,zfunc(27))
length(repvect[repvect == T])/10000
```

### d)
Theoretically, the proportion resulting from part c should be 1 as the sample is defined as a perfect normal distribution with a mean of 99.5. This means that a z-test of a random sample of values from the normal distribution should always find 99.5 to be the true mean of the population, however with a smaller sample size it can be hard to prove with a 0.05 significance level.

### e)
```{r}
prop <- function(x){
vectprop<- replicate(10000,zfunc(x))
length(vectprop[vectprop == T])/10000
}
prop(9)
prop(27)
prop(51)
```

### f)
```{r}
sapply(3:51, prop)
```

### g)
Sample size does not appear to have an effect on the results of each sample size, though it should as the sample size is used within the zscore equation.

\newpage
## Problem 2

### a)
```{r}
setwd("/Users/noahmcintire/Desktop/STAT 3080")
nym2019<-read.table("nym2019.txt", header=TRUE)
head(nym2019)
```

### b)
```{r}
vect2 <- nym2019$Time[na.rm = T]
length(vect2)
```

### c)
```{r}
vect3 <- nym2019$HomeStateOrCountry[nchar(nym2019$HomeStateOrCountry) == 2]
length(vect3)
```
Since all us states and territories only have two character length acronyms, this allowed me to subset the data by using nchar.

### d)
```{r}
usrun <- length(vect3)
vect4<-nym2019$HomeStateOrCountry[nchar(nym2019$HomeStateOrCountry) == 3]
vect5<-replicate(usrun, "US")
vect4<-c(vect4, vect5)
table(vect4)
```

### e)
```{r}
length(unique(vect4))
```

### f)
```{r}
age <- nym2019$Age
quantile(age)
```
The Youngest finisher was 21 and the oldest finisher was 71.

\newpage
### g)
```{r}
speed <- nym2019$Time
print(quantile(speed))
```


```{r}
frow<-nym2019[nym2019$Time== 130.650,]
srow<-nym2019[nym2019$Time==251.280,]
vect6<-c(frow$Age, srow$Age)
vect6
```
The fastest finisher finished was 23 years old the the slowest finisher was 41 years old.

### h)
```{r}
place <- nym2019$DivPlace[nym2019$DivPlace <= 20]
length(place)
```

### i)

```{r}
top20<-nym2019[nym2019$DivPlace <= 20,]
div<-sort(unique(top20$DIV))
div
```
\newpage
### j)
```{r}
top5 <- nym2019[nym2019$DivPlace <= 5,]
top5
```

### k)
```{r}
notq <- nym2019[nym2019$BostonQualifier == "N",]
yesq <- nym2019[nym2019$BostonQualifier == "Y",]
mean(notq$Age)
mean(yesq$Age)
```


\newpage


## References
1.<http://uc-r.github.io/na_exclude>

2.<https://rdrr.io/r/base/nchar.html>

3.<https://www.geeksforgeeks.org/sorting-of-arrays-in-r-programming/>


