---
title: "Homework 2" 
author: "Noah McIntire"
fontsize: 12pt
geometry: margin=1in
urlcolor: black
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, highlight=FALSE)
```

## Problem 1  
### a
```{r}
commutes <- matrix(c(25,22,36,23,21,36,34,33,25,32), nrow=5, ncol=2, byrow=TRUE)
commutes
```
### b
```{r}
rownames(commutes) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
colnames(commutes) <- c("Week1", "Week2")
commutes
```
\newpage
### c
On Monday, Tuesday, and Thursday she arrived faster when leaving at 8:30am. On Wednesday and Friday she arrived faster when leaving at 8:30am. 
### d
```{r}
avg_time<-apply(commutes, 1,mean)
avg_time
```

### e
```{r}
diff <- commutes -27
diff
```


### f

```{r}
avg_diff<-apply(diff, 2,mean)
avg_diff
```

### g

```{r}
max_delay<-apply(diff, 2,max)
max_delay
```


### h

```{r}
Under_half<- commutes[commutes[,"Week2"] > 30,]
Under_half<-Under_half[,2]
Under_half<-names(Under_half)
Under_half
```

### i
She arrived within her budgeted window on Monday, Wednesday, and Friday during the first week, and arrived within her window on Monday and Tuesday of the second week.

### J

```{r}
## She arrived fastest on Wednesday during the first week, which is the third row
fast<- rownames(commutes)
fast=fast[3]
fast
```

### k

```{r}
diff_sub <- diff[c(1,4),]
diff_sub
```

\newpage
## Problem 2

### a
```{r}
library("car")
require("car")
weight.metric <-Davis[,c(2,4)]
head(weight.metric)
```

### b

```{r}
weight.imp <- weight.metric * 2.2
head(weight.imp)
```

### c

```{r}
height.metric <- Davis[,c(3,5)]
head(height.metric)
```

### d

```{r}
height.imp <- round(height.metric /2.54, 1)
head(height.imp)
```

### e

```{r}
Davis.imp <- data.frame(Davis$sex, weight.imp, height.imp )
colnames(Davis.imp)<- c("sex", "rec.weight",
"rep.weight", "rec.height", "rep.height")
head(Davis.imp)
```

### f

```{r}
summary(Davis.imp)
```
There are 34 total NA values.

### g

```{r}
# From https://discuss.analyticsvidhya.com/t/how-to-count-the-missing-value-in-r/2949/5
rowSums(is.na(Davis.imp))
```
There are 19 rows with values missing.

### h

```{r}
#From: https://stackoverflow.com/questions/7980622/subset-of-rows-containing-na-missing-values-in-a-chosen-column-of-a-data-frame
sex_subset <- Davis.imp[rowSums(is.na(Davis.imp)) > 0,]
sex_subset <- sex_subset$sex
sex_subset
```
\newpage
## Problem 3

### a

```{r}
name<- c("Mercury","Venus","Earth","Mars","Jupiter","Saturn","Uranus","Neptune")
distance<-c(0.39,0.72,1,1.52,5.2,9.54,19.18,30.06)
type<-c("terrestrial","terrestrial","terrestrial","terrestrial","gas","gas","gas","gas")
diameter<-c(0.382,0.949,1,0.532,11.209,9.449,4.007,3.883)
rotation<-c(58.64,-243.02,1,1.03,0.41,0.43,-0.72,0.67)
rings<-c(F,F,F,F,T,T,T,T)
moons<-c(0,0,1,2,79,53,27,14)
solar_system<-data.frame(name, distance,
type, diameter, rotation, rings, moons)
solar_system
```

### b

```{r}
dia_l5<-solar_system[which(solar_system["diameter"] < 5),]
dia_l5
```

### c

```{r}
neg_rot<-solar_system[which(solar_system["rotation"] < 0),]
neg_rot$distance
```

### d

```{r}
dia_great<-solar_system[which(solar_system["diameter"] > 1),]
dia_great<-dia_great[,c(1,6,3)]
dia_great
```

### e

```{r}
moons_2<-solar_system[which(solar_system["moons"] > 1),]
moons_2<-moons_2[,c(6,2)]
moons_2
```

## References
1. <https://www.statmethods.net/input/missingdata.html>
2. <https://discuss.analyticsvidhya.com/t/how-to-count-the-missing-value-in-r/2949/5>
3. <https://stackoverflow.com/questions/7980622/subset-of-rows-containing-na-missing-values-in-a-chosen-column-of-a-data-frame>
