---
title: "Homework 1" 
author: "Noah McIntire"
fontsize: 12pt
geometry: margin=1in
urlcolor: black
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, highlight=FALSE)
```

## Problem 1   
### a)
```{r}
seq(to=4835,from=4751,by=7)
## Your code goes here without the ## in front.
# A citation of used code goes here with the # in front.
```
### b)
```{r}
rep("Night",4)
```
### c)
```{r}
seq(to=101,from=89,by=1)
```

### d)
```{r}
rep(21:18, c(3,3,3,3))
```

### e)
```{r}
seq(to=57,from=75,by=-3)
```

### f)
```{r}
c(seq(to=75,from=25,by=10),seq(to=50,from=70,by=-5))
```

### g)
```{r}
rep(seq(to=500,from=400,by=25),5:1)
```

### h)
```{r}
rep(3:1,5)
```

### i)
```{r}
c(seq(to=68,from=124,by=-8),seq(to=38,from=63,by=-5))
```

### j)
```{r}
rep(c("Morning","Afternoon","Night"),2)
```
\newpage
## Problem 2  
### a)
```{r}
dnorm(26.24, mean=63, sd=11)
```
 There is a .01% chance that this time is beaten in this race.
### b)
```{r}
qnorm(0.05, mean=63, sd=11)
```
The target time for the runner should be any time under 44.9 minutes.
### c)
```{r}
#29000 runners
29000* (1-pnorm(90, mean=63, sd=11))
```
Around 205 runners will likely have their races disrupted by the resumption of traffic.

## Problem 3
### a)
```{r}
lie_1 = 1-pbinom(0,12,0.2)
lie_1
```

### b)
```{r}
vect_num_lie = 0:11
lie_new <- 1-pbinom(vect_num_lie,12,0.2)
lie_new <- round(lie_new, 3)
lie_new
```

### c)
```{r}
lie_3 = lie_new
lie_3Matrix = rbind(vect_num_lie, lie_3)
lie_3Matrix
```
The column names are confusing in this case as they are one of from the number of successes in this data set. 

### d)
```{r}
names(lie_new) = vect_num_lie
lie_new
```

### e)
The presentation method in section d is much easier to read and understand what it is trying to convey, even though it is missing row names.

\newpage
### f)
```{r}
data_lie <- data.frame(vect_num_lie, lie_new)
data_lie
```

### g)
```{r}
data_lie2 = data.frame(lie_new)
data_lie2
```

### h)
The data frame created in 3f is a better presentation of the data. While the number repeat, it still includes a column name that allows the viewer to interpret what it means, which is not possible with the data frame created in 3g.

## Problem 4
```{r}
course_data = data.frame(Course1 = '"Stat 2559"', Course2 ='"Stat 3080"', row.names = "")
Course1 <- list(5)
Course2 <- list(75, 90, 90)
teach_data = data.frame(Course1 = FALSE, Course2 = TRUE, row.names = "")
myList <- list(Name = "Gretchen Martinet",
               Department= "Statistics",
               Courses= course_data, ActiveTeach = teach_data,
               Enr = list(Course1 = 5, Course2 = c(75, 90, 90)), Days = list( Course1 = c("Tuesday", "Thursday"), Course2 =cbind(c("Monday", "Tuesday", "Tuesday"), c("Wednesday", "Thursday", "Thursday"))
              
                                                                              ))
print(myList)
```

## References
1. <https://stackoverflow.com/questions/24428051/removing-display-of-row-names-from-data-frame>
2. <https://stackoverflow.com/questions/22234368/creating-a-matrix-from-multiple-column-vectors>
3. <https://stackoverflow.com/questions/10776742/how-can-i-make-a-list-of-lists-in-r>

