---
title: "Project Part 3" 
fontsize: 12pt
geometry: margin=1in
urlcolor: black
output: pdf_document
header-includes:
- \usepackage{setspace}
- \onehalfspacing
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, highlight=FALSE)
```

```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
library(tidyverse)
## Use this chunk for reading in packages.
## Use this chunk for reading in the data, combining the data, and any other major data cleaning that is not relevant to show.
pd.read
## Remove the ## before all code.
```

## Research Question
Based on the primary source data found on this info, The research question most relevant would be:
Research question here.

Rubric: At least one research question is clearly stated at the beginning of the report.

## Data Explanation
Rubric: General context of the data, including the primary sources used to create the data, is given and explained well.

## Data Classification
Rubric: Whether the data are a sample or population is clearly and correctly stated.

## Data Collection
Rubric:  The collection (and, if the data are a sample, selection) methods that were used by the primary sources are given and explained in detail.

## Data Contents
Rubric: Explanation of the specifics of the data is given and clear. It is clear what the observations are and what relevant information is recorded for each.

## Data Issues
Rubric: At least one potential issue with the data is given and thoroughly explained. (for osha explain why it isnt a representative sample)

## Data Appropriateness
Rubric: Explanation of how the data described are appropriate to address the research question(s) is given and clear.

## Numerical Summary Presence
Rubric: At least one appropriate and correctly coded numerical summary that does not show counts is given.

## Numerical Summary Relevance
Rubric: The one (or more) numerical summary that does not show counts provides relevant information and can be clearly understood.

## Graphical Summary Presence
Rubric:At least one appropriate and correctly coded graphical summary that does not show counts is given.

## Graphical Summary Relevance
Rubric: The one (or more) graphical summary that does not show counts provides relevant information and can be clearly understood due to comprehensive, descriptive labels.

## Conclusion
Rubric: At least one appropriate and clearly articulated conclusion is drawn.


Report length: Fewer than 7 pages

References are cited at end and throughout the project




### Subsection headers, if using
Your text.

Linebreaks are created using two spaces at the end of the previous line of text, or using the command \newline.  
Pagebreaks are created using the command \newpage.  
Note: These commands execute when knitting, moving the end-of-sentence period in the resulting PDF.

```{r}
## R code to be shown. 
## Remove the ## before all code.
```


## References
1. Your resources go here. Links should be surrounded by <>.
